Significant declines in standardised test scores due to COVID-19 school closures disproportionately affect vulnerable students: A replication analysis using data from the United States and a case study on the Netherlands

### 2024-02-14 paper/paper.qmd
Updated citation
Updated a citation in the qmd and paper

Finally, data from “Pandemic	Schooling	Mode	and	Student	Test	Scores:	Evidence	from	US	School Districts” [@TestScore] was used to examine changes in district-level pass rate data from 11 state standardised assessments, taken in the spring of 2018, 2019 and 2021. Both @fig-mathscoresbyonline and @fig-elascoresbyonline both provide information on the change in pass rates in Math and ELA standardised tests from the previous year, respectively, taking into account the share of in-person learning done by various school districts and across the three years of interest, each indicated by its respective color. Consistent with Jack and Oster [-@Jack_Oster_2023], our analysis shows a significant decline in pass rates from the 2018-2019 to the 2020-2021 school year. We see that in Spring 2021, there is a clear fall in the pass rates overall in both subject areas from 2019 (note that there were no standardised assessmments in 2020), though this fall is much more pronounced in Math than ELA (-12.8 percentage points compared to the -6.8 percentage points, respectively). The discrepancy between these two subjects is consistent with much of the current economic literature, which shows mathematics scores to be more sensitive to schooling differences [@betts2011effect; @angrist].

>>>>

Finally, data from “Pandemic	Schooling	Mode	and	Student	Test	Scores:	Evidence	from	US	School Districts” [@Jack_Oster_2] was used to examine changes in district-level pass rate data from 11 state standardised assessments, taken in the spring of 2018, 2019 and 2021. Both @fig-mathscoresbyonline and @fig-elascoresbyonline both provide information on the change in pass rates in Math and ELA standardised tests from the previous year, respectively, taking into account the share of in-person learning done by various school districts and across the three years of interest, each indicated by its respective color. Consistent with Jack and Oster [-@Jack_Oster_2023], our analysis shows a significant decline in pass rates from the 2018-2019 to the 2020-2021 school year. We see that in Spring 2021, there is a clear fall in the pass rates overall in both subject areas from 2019 (note that there were no standardised assessmments in 2020), though this fall is much more pronounced in Math than ELA (-12.8 percentage points compared to the -6.8 percentage points, respectively). The discrepancy between these two subjects is consistent with much of the current economic literature, which shows mathematics scores to be more sensitive to schooling differences [@betts2011effect; @angrist].
